---
fontsize: 11pt
geometry: margin=1in
output:
  pdf_document:
    number_sections: yes
spacing: single
---
\newgeometry{margin=1.5in}
\begin{titlepage}
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}} 
\center
\textsc{\LARGE University of California, Santa Barbara}\\[1.5cm]
\textsc{\Large MATH 104B}\\[0.5cm]
\textsc{\large FINAL PROJECT}\\[0.5cm] 
\vspace{2cm}
\HRule \\[0.4cm]
{\Large\bfseries An Application of Numerical Analysis to the COVID-19 Spread in Hubei, China}\\[0.4cm] 
\HRule \\[1.5cm]
\vspace{2cm}
\begin{minipage}{0.4\textwidth}
\begin{flushleft} \large
\emph{Authors:}\\
Emily \textsc{Lu}\\
Alberto \textsc{Beltran}\\
Matthew \textsc{Peters}
\end{flushleft}
\end{minipage}
~
\begin{minipage}{0.4\textwidth}
\begin{flushright} \large
\emph{Supervisor:} \\
Professor Paul \textsc{Atzberger} % Supervisor's Name
\end{flushright}
\end{minipage}\\[1.5cm]
\vspace{4cm}
{\large March 4th, 2020}\\[0.5cm]

{\large }

\vfill 

\end{titlepage}
\restoregeometry

\newpage 
```{r setup, include=FALSE}
library(reticulate)
pd <- import("pandas")
math <- import("math")
```

\section*{Abstract}

The background area being discussed is the COVID-19 disease and specifically modeling the number of people infected as a whole within the Hubei Province. Using data gathered from the World Health Organization (WHO) and taking into account the number of cases reported, the contagion rate, and the total population, we are able to model the number of individuals infected with the COVID-19 disease compared to the reported number of confirmed cases. In this project, we aim to determine the number of individuals in the Hubei Province infected with the disease compared to the number of reported cases, which allows us to determine the reproductive ratio of the disease. The methods used to solve the question at hand will be Numerical Linear Matrix operations, and approximating the Adam Moulton methods using the exponential growth formula.

\thispagestyle{empty}

\newpage
\tableofcontents
\thispagestyle{empty}
\newpage
\clearpage
\pagenumbering{arabic}

\section{Introduction} 

The objectives are to understand better the mathematical dynamics of an infected population when an outbreak occurs. Another goal is to use mathematical modeling to examine and to analyze the viral dynamics of the COVID-19 disease. To model this outbreak, the systems of differential equations are used. We decided to model the COVID-19 disease in the Hubei Province in February 2020 and compare the disease spread using an SIR model. 

The purposes of this research are:

1. To apply SIR model to predict the outbreaks of COVID-19 virus.

2. To determine the effect of the initial number of infected individuals of the population.

\section{Modeling the Spread of Infected}

The COVID-19 disease has been present for 1 month in the Hubei Province. According to reports, the disease has an average natural lifespan of 30 days. The contagion rate for the first 10 days is 1.9, the contagion rate for the next 10 days is 2.6, and the contagion rate for the last ten days is 3.6. We reported the total number of confirmed cases at 10 day intervals for a month (30 days) in an effort to compute the ratio of infected (with respect to the total population). According to WHO, the population of Hubei is approximately 59 million people. Thus, we took 59 million as the fixed population of Hubei and gathered the daily number of new cases from February 1st, 2020 to March 2nd, 2020. Using these figures, we calculated the average number of cases reported within the first 10 days to be 2247.8, the average number of cases within the next 10 days to be 1325.7, and the average number of cases within the last ten days to be 464.5. Afterwards, we divided each values by the total population and set it as the first row of matrix $A$. Using these informations, we generated a rough estimate of the actual number of people infected by taking into account the spread factor of the disease by using the following steps below: 


Step 1: Define matrix $A$. 

A matrix $A=[a_{ij}]$ can be used to model the COVID-19 disease transmission rate (based on the number of cases reported, the contagion rate, and the total population after adjusting for fatalities) by letting $a_{ij}$ denote the probability that an infected person from the $i$th time period transmitted the COVID-19 disease to a susceptible person in the $j$th time period. With this in mind, we could solve for the first row of matrix $A$ which contains the averaged contagion rates of each time interval based on actual number of cases. 

According to WHO based on the situation reports in February 2020, the "incubation period" or the time frame between catching COVID-19 and beginning to have symptoms of the disease could range from 2-10 days. Thus, we selected 10 days to the possible time period an infected person could have spreaded the disease to others since we were working with data over a 30-days period. With the first 10 days being the possible incubation period, we solved for the following: 

* $a_{21}$ which is determined by adding the confirmed cases from 1-10 days and 10-20 days, then multipying by the contagion rate 2.6 followed by dividing the respective total population and 

* $a_{32}$ which is determined by adding the confirmed cases from 10-20 days and 20-30 days, then multipying by the contagion rate 3.1 followed by dividing the respective total population. 

\begin{center} 
$A$ = 
$\begin{bmatrix}
0.00038098 & 0.0002247 & 0.00007873 \\
0.0015747801 & 0 & 0 \\
0 & 0.0009406356 & 0
\end{bmatrix}$
\end{center}


Step 2: Define matrix $x$ and solve for vector $b$. 

Vector $x$ is population per time period (10 days) which was found by re-evaluating each row following the first by taking into account the number of deaths from the prior 10 days. 

Vector $b$ is average number of reported / population per 10 days. Therefore, vector $b$ has the following rows:
\begin{eqnarray} b_{11}&:&\text{ total number of confirmed cases over 30 days.} \\
b_{21}&:&\text{ total number of infected after 20 days.} \\
b_{31}&:&\text{ total number of infected after 30 days.}\end{eqnarray} 

Our goal was then to solve for vector $b$ through the matrix multiplication of $Ax$.
\begin{eqnarray} \begin{bmatrix} 0.00038098 & 0.0002247 & 0.00007873 \\ 0.0015747801 & 0 & 0 \\ 0 & 0.0009406356 & 0 \end{bmatrix} \begin{bmatrix} 59000000 \\ 58999350 \\ 58998618 \\ \end{bmatrix} = \begin{bmatrix} 40379.93514014 \\ 92912.0259 \\ 55496.88898686 \\ \end{bmatrix} \end{eqnarray}

From the results of vector $b$, we could see that number of people infected drastically increased from the first and second time interval, but decreased from the second to third time interval. This is plausible because the Hubei Province started their quarantine process in late January and thus, decreased the contagion rate of the COVID-19 disease. 

Step 3: Use the exponential growth formula to measure the rate of spread of the disease in 1 month in advance. 

Since the COVID-19 disease is an airborne virus, we applied the explonential growth formula, using $b_{31}=55496$ as the initial number of infected since $b_{31}$ is denoted as the most "current" in our case, to approximate number of infected people in the future. We modeled this as $$y=55496e^{2t}$$ and we adapted this solution to an initial value problem, $$f(t,y) = 2ye^{2t}.$$ This initial value problem $f(t,y)$ is used to find our exponential growth approximations through the Runge-Kutta and Adam Moulton methods. 

```{python, echo = FALSE}
import numpy as np 
import pandas as pd

# Matrix model of the proportion of people infected as a whole  
A = [[0.00038098, 0.0002247, 0.00007873],
   [0.0015747801, 0, 0],
   [0, 0.0009406356, 0]]

# Matrix model of the population per time period
x = [[59000000],
   [58999350],
   [58998618]]

# Matrix model of the total population infected per time period
b = np.matmul(A, x)

# Time sequence array of size N 
def t_i():
    t = np.zeros(n+1)
    t[0] = a 
    for i in range(n):
        t[i+1] = t[i] + h 
    return t 

# Runge Kutta 4-Step method; used to estimate the first 
# few values for the Adams Moulton methods  
def rk4(n):
    w = np.zeros(n+1)
    w[0] = alpha 
    for i in range(n):
        k1 = h*f(t[i], w[i])
        k2 = h*f(t[i] + h/2, w[i] + k1/2)
        k3 = h*f(t[i] + h/2, w[i] + k2/2)
        k4 = h*f(t[i] + h, w[i] + k3)
        w[i+1] = w[i] + 1/6*(k1 + 2*k2 + 2*k3 + k4)
    return w 

# Adams Moulton 2-Step Method
def adamsMoult_2(y): 
    w = np.zeros(n+1)
    w[0], w[1], w[2] = y[0], y[1], y[2]
    for i in range(2, n):
        w[i+1] = w[i] + h/12*(5*f(t[i+1], w[i+1]) + 8*f(t[i], w[i])
                - f(t[i-1], w[i-1]))
    return w

# Adams Moulton 3-Step Method
def adamsMoult_3(y):
    w = np.zeros(n+1)
    w[0], w[1], w[2], w[3] = y[0], y[1], y[2], y[3]
    for i in range(3, n):
        w[i+1] = w[i] + h/24*(9*f(t[i+1], w[i+1]) + 19*f(t[i], w[i])
                - 5*f(t[i-1], w[i-1]) + f(t[i-2], w[i-2]))
    return w

# Adams Moulton 3-Step Method
def adamsMoult_4(y):
    w = np.zeros(n+1)
    w[0], w[1], w[2], w[3], w[4] = y[0], y[1], y[2], y[3], y[4]
    for i in range(4, n):
        w[i+1] = w[i] + h/720*(251*f(t[i+1], w[i+1]) 
                + 646*f(t[i], w[i]) - 264*f(t[i-1], w[i-1])
                + 106*f(t[i-2], w[i-2]) - 19*f(t[i-3], w[i-3]))
    return w 

# Iterative function that solves the function y
# at each value in the time array t
def actual(n):
    solutions = []
    for i in range(n+1):
        solutions.append(y(t[i]))
    return solutions 

# Initial value problem  
def f(t,y):
    return (2*y*np.e**(2*t))

# Solution to the initial value problem above 
def y(t):
    return(55496*np.e**(2*t))

alpha = 55496; h = 0.05; a = 0; n = 20; t = t_i()

data = {'Runge Kutta 4-Step':rk4(n),
        'AM 2-Step':adamsMoult_2(rk4(2)), 
        'AM 3-Step':adamsMoult_3(rk4(3)),
        'AM 4-Step':adamsMoult_4(rk4(4)),
       'Actual':actual(n)}

table = pd.DataFrame(data).round()
table.index = t
table.index.name = 'Time'
```
```{r, echo=FALSE}
library(knitr)
kable(py$table)
```


\section{Modeling the COVID-19 as a SIR Model}

We used the SIR model to illustrate the transfer of the epidemic disease through the interaction of the following three different variables: 

>$S$ = Number of people that are susceptible to COVID-19 
>$I$ = Number of people infected with COVID-19 
>$R$ = Number of people recovered from COVID-19 with total immunity

For simplicity, we assumed a fixed population of $N$ people, where
$$N = S + I + R;$$
in other words, there will be no births or deaths taken into account. 

The SIR model uses 3 differential equations:
\begin{eqnarray} \frac{dS}{dT} = -\beta IS; \; \frac{dI}{dT} = \beta IS - \gamma I; \; \frac{dR}{dt} = \gamma I \end{eqnarray} where $S(t)$ is the number of susceptible people in the population at time $t$, $I(t)$  is the number of infectious people at time $t$, $R(t)$ is the number of recovered people at time $t, \beta$ is the transmission rate, $\gamma$ represents the recovery rate. Note: in our SIR model, we set $t$ = 0 for the start of February 2020.

Now given our research on the COVID-19 outbreak in the Hubei Province from February 1st, 2020 to March 2nd, 2020 through WHO, we assigned the parameters with the following values: 

> $N = 59000000$ which is the total population of Hubei, 
> $I = 40380$ which is the number of people infected in the month of February,

and solved for the rest. 

The number of people dead in the month of February is 1382. However, seeing as $R$ includes the number of people who have received permanent immunity, this could be simplified to include those who have died as they'll have permanent immunity afterwards and those who have recovered with permanent immunity. Therefore, number of people recovered could be defined as $R = 1382 + (0.6\times 40380) = 25,610.$

The duration of the disease ranges from 1 to 30 days [10]; therefore we could roughly estimate the duration of the disease at the midpoint, i.e.15 (approx.) days:

$D = 15; \; \gamma = 1/15 = 0.067.$

According to WHO, the mortality rate of COVID-19 is 0.4 [3] and the total population of the Hubei Province after accounting for deaths is 58,998,618. Therefore, $\beta$ (the rate of infection) $=0.4/ 58,998,618 = 6.7798 \times 10^{-9}, \; S=58932628,$ and $N=58,998,618$.  

In order to use the SIR model to predict the evolution of the disease, it would be helpful if we could solve the system of differential equations. Therefore, we used numerical approaches such as the fourth order Runge-Kutta method to extract the solution. 

```{python, echo = FALSE}
import numpy as np 
import pandas as pd

# SIR model version of the Runge Kutta 4-Step method  
def rk4_SIR(n):
    S = np.zeros(n+1); I = np.zeros(n+1); R = np.zeros(n+1)
    S[0] = alpha0; I[0] =  alpha1; R[0] = alpha2 
    
    dSdt = lambda S, I: -beta*S*I
    dIdt = lambda S, I: beta*S*I - gamma*I
    dRdt = lambda I: gamma*I
    
    for i in range(n):
        N = S[i] + I[i] + R[i]
        
        k1_S = dSdt(S[i], I[i])
        k1_I = dIdt(S[i], I[i])
        k1_R = dRdt(I[i])
        
        k2_S = dSdt(S[i] + k1_S*h/2, I[i] + k1_I*h/2)
        k2_I = dIdt(S[i] + k1_S*h/2, I[i] + k1_I*h/2)
        k2_R = dRdt(I[i] + k1_I*h/2)
        
        k3_S = dSdt(S[i] + k2_S*h/2, I[i] + k2_I*h/2)
        k3_I = dIdt(S[i] + k2_S*h/2, I[i] + k2_I*h/2)
        k3_R = dRdt(I[i] + k2_I*h/2)
        
        k4_S = dSdt(S[i] + k3_S*h, I[i] + k3_I*h)
        k4_I = dIdt(S[i] + k3_S*h, I[i] + k3_I*h)
        k4_R = dRdt(I[i] + k3_I*h)
        
        S[i+1] = S[i] + h/6*(k1_S + 2*k2_S + 2*k3_S + k4_S)
        I[i+1] = I[i] + h/6*(k1_I + 2*k2_I + 2*k3_I + k4_I)
        R[i+1] = R[i] + h/6*(k1_R + 2*k2_R + 2*k3_R + k4_R)
        
    return S, I, R 

alpha0 = 58932628; alpha1 = 40380; alpha2 = 25610    
h = 1; a = 0; n = 30; t = t_i(); beta =  0.4/58998618; gamma = 1/15
S, I, R = rk4_SIR(n)

data = {'Susceptible (S)':S,
    'Infectious (I)':I,'Recovered (R)':R, 'Population (N)': S + I + R}
SIR_table = pd.DataFrame(data).round()
SIR_table.index = t
SIR_table.index.name = 'Time'
```
```{r, echo = FALSE}
kable(py$SIR_table)
```

\section{Initial Value Problem Analysis}
The proposed differential equations with, $$0\leq\beta\leq 6.778*10^{-9}, \quad 0\leq\gamma\leq .067$$ are:
\begin{equation} \frac{dS}{dt} = -\beta IS \\ \frac{dI}{dt} = \beta IS - \gamma I \\ \frac{dR}{dt} = \gamma I. \end{equation}
 
To illustrate the robustness of these differential equations, we will aim to satisfy a Lipschitz condition and show their well-possedness. 

Define
    $$D = {[(t,S,I,R)| \quad 0\leq t \leq 30, \quad and \quad -\infty<S, I, R<\infty]}$$
\textbf{Equation (1)}: 
$$\frac{dS}{dt} = -\beta IS = f(t, S, I)$$
And so
$$|f(t, S_1, I_1) - f(t, S_2, I_2)| = \beta |I_2S_2 - I_1S_2| \leq6.778*10^{-9}|I_2S_2 - I_1S_2|.$$
The equation then satisfies a Lipschitz condition with constant $$L=6.778*10^{-9}.$$
In addition, $f(t, S, I)$ is clearly defined everywhere on $D$. So by Theorem 5.6, we know that (1) is well-posed.

\textbf{Equation (2)}: 
$$\frac{dI}{dt} =\beta IS - \gamma I = f(t, S, I)$$
And so
$$|f(t, S_1, I_1) - f(t, S_2, I_2)| = |\beta(I_1S_1-I_2S_2)+\gamma(I_2-I_1)|\leq\beta|I_1S_1-I_2S_2|+\gamma|I_2-I_1|$$
Now let $$L=max(|\beta|,|\gamma|).$$
Hence, $$f(t, S_1, I_1) - f(t, S_2, I_2) \leq L(|I_1S_1-I_2S_2|+|I_2-I_1|).$$
And (2) then satisfies a Lipschitz condition with constant $$L=\gamma=.067.$$
In addition, $f(t, S, I)$ is clearly defined everywhere on $D$. So by Thm. 5.6 we know that (2) is well-posed.

\textbf{Equation (3)}:
$$\frac{dR}{dt} =\gamma I = f(t, S, I)$$
And so
$$|f(t, S_1, I_1) - f(t, S_2, I_2)| = \gamma|I_1-I_2| \leq .067|I_1-I_2|.$$
The equation then satisfies a Lipschitz condition with constant $$L=.067.$$
In addition, $f(t, S, I)$ is clearly defined everywhere on $D$. So by Thereom 5.6 from the *Numerical Analysis 10 Ed.*, we know that (3) is well-posed.

\section{Concluding Remarks}

In this project, our objective was to mathematically model the number of people infected with the novel COVID-19 disease. More specfically, we wanted to first simulate the number of people infected through a mathematical model compared to the reported number of reported cases from WHO's February 1st, 2020 to March 2nd, 2020 situation reports. To do so, we utilized the Numerical Linear Matrix operations and then, the Adam Moulton methods. We found the next month results through the Adams Moulton methods to significantly vary from the supposed actual reported cases. A plausible explanation for this is that these numerical methods do not take into account of the quarantine effect on the contagion rate of the disease. With in this mind, we then decided to model the problem as SIR model instead. We started by defining an SIR model representation of the COVID-19 by finding the initial value problem. After, simulating our SIR model using exponential growth and the Runge-Kutta 4th order method, we found our number of infected people not too far off from our Runge-Kutta values we obtained in the first part of our project. Since the initial value problem we defined for our SIR model which was obtained by observing a physical phenomena generally only approximate the true situation, we wanted to know whether a small change in the statement of our problem would also introduce correspondingly small changes. To do so, we tested for the well-posedness of our problem and found that it is well-posed. Thus, we concluded that our SIR model is a valid representation of the COVID-19 disease transmission spread. However, given the nature of our model, it is not a perfect representation as it does not take into account the number of deaths, the immunity rate, and other control factors we may have been shortsighted with. Overall, it was interesting to learn how numerical analysis could be used to mathematically model the possible contagion rates if the government of China did not step in to quarantine their people in the Hubei Province. 

\newpage
\addcontentsline{toc}{section}{Appendix: Additional Python Code}
\section*{Appendix: Additional Python Code}
\thispagestyle{empty}
```{python}
import numpy as np 
import pandas as pd

# Matrix model of the proportion of people infected as a whole  
A = [[0.00038098, 0.0002247, 0.00007873],
   [0.0015747801, 0, 0],
   [0, 0.0009406356, 0]]

# Matrix model of the population per time period
x = [[59000000],
   [58999350],
   [58998618]]

# Matrix model of the total population infected per time period
b = np.matmul(A, x)

# Time sequence array of size N 
def t_i():
    t = np.zeros(n+1)
    t[0] = a 
    for i in range(n):
        t[i+1] = t[i] + h 
    return t 

# Runge Kutta 4-Step method; used to estimate the first 
# few values for the Adams Moulton methods  
def rk4(n):
    w = np.zeros(n+1)
    w[0] = alpha 
    for i in range(n):
        k1 = h*f(t[i], w[i])
        k2 = h*f(t[i] + h/2, w[i] + k1/2)
        k3 = h*f(t[i] + h/2, w[i] + k2/2)
        k4 = h*f(t[i] + h, w[i] + k3)
        w[i+1] = w[i] + 1/6*(k1 + 2*k2 + 2*k3 + k4)
    return w 

# Adams Moulton 2-Step Method
def adamsMoult_2(y): 
    w = np.zeros(n+1)
    w[0], w[1], w[2] = y[0], y[1], y[2]
    for i in range(2, n):
        w[i+1] = w[i] + h/12*(5*f(t[i+1], w[i+1]) + 8*f(t[i], w[i])
                - f(t[i-1], w[i-1]))
    return w

# Adams Moulton 3-Step Method
def adamsMoult_3(y):
    w = np.zeros(n+1)
    w[0], w[1], w[2], w[3] = y[0], y[1], y[2], y[3]
    for i in range(3, n):
        w[i+1] = w[i] + h/24*(9*f(t[i+1], w[i+1]) + 19*f(t[i], w[i])
                - 5*f(t[i-1], w[i-1]) + f(t[i-2], w[i-2]))
    return w

# Adams Moulton 3-Step Method
def adamsMoult_4(y):
    w = np.zeros(n+1)
    w[0], w[1], w[2], w[3], w[4] = y[0], y[1], y[2], y[3], y[4]
    for i in range(4, n):
        w[i+1] = w[i] + h/720*(251*f(t[i+1], w[i+1]) 
                + 646*f(t[i], w[i]) - 264*f(t[i-1], w[i-1])
                + 106*f(t[i-2], w[i-2]) - 19*f(t[i-3], w[i-3]))
    return w 

# Iterative function that solves the function y
# at each value in the time array t
def actual(n):
    solutions = []
    for i in range(n+1):
        solutions.append(y(t[i]))
    return solutions 

# Initial value problem  
def f(t,y):
    return (2*y*np.e**(2*t))

# Solution to the initial value problem above 
def y(t):
    return(55496*np.e**(2*t))

alpha = 55496; h = 0.05; a = 0; n = 20; t = t_i()

data = {'Time':t, 'Runge Kutta 4-Step':rk4(n),
        'Adams Moulton 2-Step':adamsMoult_2(rk4(2)), 
        'Adams Moulton 3-Step':adamsMoult_3(rk4(3)),
        'Adams Moulton 4-Step':adamsMoult_4(rk4(4)),
       'Actual':actual(n)}

table = pd.DataFrame(data).round()

# SIR model version of the Runge Kutta 4-Step method  
def rk4_SIR(n):
    S = np.zeros(n+1); I = np.zeros(n+1); R = np.zeros(n+1)
    S[0] = alpha0; I[0] =  alpha1; R[0] = alpha2 
    
    dSdt = lambda S, I: -beta*S*I
    dIdt = lambda S, I: beta*S*I - gamma*I
    dRdt = lambda I: gamma*I
    
    for i in range(n):
        N = S[i] + I[i] + R[i]
        
        k1_S = dSdt(S[i], I[i])
        k1_I = dIdt(S[i], I[i])
        k1_R = dRdt(I[i])
        
        k2_S = dSdt(S[i] + k1_S*h/2, I[i] + k1_I*h/2)
        k2_I = dIdt(S[i] + k1_S*h/2, I[i] + k1_I*h/2)
        k2_R = dRdt(I[i] + k1_I*h/2)
        
        k3_S = dSdt(S[i] + k2_S*h/2, I[i] + k2_I*h/2)
        k3_I = dIdt(S[i] + k2_S*h/2, I[i] + k2_I*h/2)
        k3_R = dRdt(I[i] + k2_I*h/2)
        
        k4_S = dSdt(S[i] + k3_S*h, I[i] + k3_I*h)
        k4_I = dIdt(S[i] + k3_S*h, I[i] + k3_I*h)
        k4_R = dRdt(I[i] + k3_I*h)
        
        S[i+1] = S[i] + h/6*(k1_S + 2*k2_S + 2*k3_S + k4_S)
        I[i+1] = I[i] + h/6*(k1_I + 2*k2_I + 2*k3_I + k4_I)
        R[i+1] = R[i] + h/6*(k1_R + 2*k2_R + 2*k3_R + k4_R)
        
    return S, I, R 

alpha0 = 58932628; alpha1 = 40380; alpha2 = 25610    
h = 1; a = 0; n = 30; t = t_i(); beta =  0.4/58998618; gamma = 1/15
S, I, R = rk4_SIR(n)

data = {'Susceptible (S)':S,
    'Infectious (I)':I,'Recovered (R)':R, 'Population (N)': S + I + R}
SIR_table = pd.DataFrame(data).round()
```

\newpage
\addcontentsline{toc}{section}{Reference}
\section*{Reference}
\bibliographystyle{acm}
\bibliography{ref}
Numerical Analysis 10th Ed. by R. Burden, J. D. Faires, A. M. Burden

“Novel Coronavirus (2019-NCoV) Situation Reports.” _World Health Organization_, World Health Organization, 2020, www.who.int/emergencies/diseases/novel-coronavirus-2019/situation-reports.
